Decision Support Phase
========================================================

This phase takes estimates of the sensitivity (detection probability) of each monitoring method used in the implementation phase and calculates the number of repeat monitorings required to confirm eradication.  It is assumed that the number of devices (and nights) set for each method is set by the user.  Also the stopping rule criterion needs to be set by the user.  Here the stopping rule is based on minimising the type I error rate (probability of failure).

### Read in estimates

Read in the latest estimates of monitoring detection parameters from the implementation phase.  This will usually be from the last update when nominal eradication was declared

```{r read_est, echo=TRUE, results='hide'}
# Loading analysis toolset
source("Framework functions.r")
library(spatstat,quietly=T,verbose=F)
library(maptools,quietly=T,verbose=F)

region<- readShapeSpatial("footprint") # Insert ARCgis shapefile filename here
region<- as.owin.SpatialPolygons(region[1,]) # index 1 for main island and ignore small islands
region<- rescale(region,3.28083) #convert feet to meters

# Loading latest updated analysis results (change filename below)
filename<- "rem1" 
load(filename)
load("roads") # this would normally be a shapefile
```

### Set parameters for the decision support monitoring

The following parameters required user input

```{r setparams,echo=FALSE}
ncams=30
cat(paste("Maximum cameras set at ",ncams),"\n")
nsign=200
cat(paste("Maximum sign survey plots set at ",nsign),"\n")
nmax<- 10
cat(paste("Maximum number of repeat surveys set at ",nmax),"\n")
Radius<- 1000
cat(paste("Effective strip width around each device set at ",Radius," meters"),"\n")
P.Fail<- 0.01
cat(paste("Stopping rule (probability of eradication failure) set at ",P.Fail),"\n")
```

```{r, echo=FALSE}
# read parameters
par1<- rem1["a2",c(1,2)]
par2<- rem1["a3",c(1,2)]

post.sens<- matrix(0,nrow=nmax,ncol=6)
post.sens[1,]<- Update.prior(par1=par1,par2=par2,prior.par=c(1,1),ncams=ncams,nsign=nsign,roads=roads,region=region,rad=Radius)

# Update
for(i in 2:nmax) {
prior.par<- post.sens[i-1,c(5,6)]  
post.sens[i,]<- Update.prior(par1=par1,par2=par2,prior.par=prior.par,ncams=ncams,nsign=nsign,roads=roads,region=region,rad=Radius)

}

post.sens<- data.frame(post.sens)
names(post.sens)<- c("mu","sd","lcl","ucl","a","b")
```

### Optimal amount of monitoring

```{r, echo=FALSE}
nmin<- min(which(post.sens$mu < P.Fail))
cat(paste("Minimum number of repeat monitors with current sample size is ",nmin),"\n")
```

### Plot results

The plot below shows the relationship between the number of repeat monitors and the probability of eradication failure.

```{r, fig.height=5,fig.width=5, echo=FALSE}
par(pty='s')
plot(1:nmax,post.sens$mu,type='l',ylim=c(0,1),xlab="repeat monitorings",ylab="Probability")
lines(1:nmax,post.sens$ucl,lty=2)
abline(h=P.Fail,lty=3,col="red")

```
