Decision Support Phase
========================================================

This phase takes estimates of the sensitivity (detection probability) of each monitoring method used and calculates the number of repeat monitorings required to confirm eradication.  It is assumed that the number of devices (and nights) set for each method is set by the user.  Also the stopping rule criterion needs to be set by the user.  Here the stopping rule is based on minimising the type I error rate (probability of pest eradication | no pests detected).

```{r setup, include=FALSE}
library(knitr)
library(raster)
library(sf)
library(tidyverse)
```
### Load functions and read in region shapefile ...

```{r}
source("Framework_functions.r")
region<- read_sf("Stuff/.","San_Nicolas_projected")

```

### Rasterize the region for spatial sampling 

```{r}
res<- 500 # cell size in meters

```

The region has been divided up into cells of size `r res` meters.  Sampling units will be assigned randomly  

```{r, echo=F, message=F}
bb<- st_bbox(region)
rast<- raster(xmn=bb$xmin,xmx=bb$xmax,ymn=bb$ymin,ymx=bb$ymax,resolution=res)
rast<- rasterize(region, rast, field=1)
rast_df<- raster_data(rast)

p1<- region %>% ggplot() +
  geom_tile(aes(x, y, fill=value), color="grey50", data=rast_df, show.legend = F) +
  scale_fill_gradientn(colors="lightblue",na.value="white") +
  geom_sf(fill=NA) +
  labs(x="Easting",y="Northing",title="Monitoring Cells in sampled region")
p1

nq<- sum(rast_df$value, na.rm=TRUE) # number of potential monitoring cells 
```

The total number of potential monitoring cells is **`r nq`**

### Set parameters for the decision support monitoring

**The following parameters require user input**

```{r setparams,echo=FALSE}
ncells<- floor(nq * 0.8)  # select proportion of available cells for monitoring
nsessions<- 20
ndays<- 20
ndevices<- 1
thresh.pfree<- 0.95
device.est<- data.frame(mean= -5, sd=2)  # logit scale per device per day
nsims<- 1000

params<- list(ntraps=ndevices, ndays=ndays, ncells=ncells, dpar=device.est)
```

The number of cells selected for monitoring is: **`r ncells`**, which is **`r round(ncells/nq*100)`**% coverage 

Maximum number of monitoring sessions set to: **`r nsessions`**

Consecutive monitoring days per session set to: **`r ndays`**

Number of devices per monitoring cell set to: **`r ndevices`**

Detection parameters for devices set to a mean of **`r device.est$mean`** with a standard deviation of **`r device.est$sd`** on the logit scale

Number of simulated monitorings undertaken: **`r nsims`**

## Set the stopping rule

Stopping rule (threshold for probability of pest eradication | none detected) set to: **`r thresh.pfree`**

*Conduct moniotring and update stopping rule*

```{r, echo=FALSE}
mat<- matrix(NA, nrow=nsessions, ncol=4)
colnames(mat)<- c("Session","P.erad","LCL","UCL")

prior.params<- list(a=1.5,b=1.5) # initial uninformative prior
res= calc.erad(rast, nsims, prior.params, params)
updated.priors<- calc.beta.parms(res$P.erad)
mat[1,]<- c(1,qbeta(0.5,1.5,1.5),qbeta(0.025,1.5,1.5),qbeta(0.975,1.5,1.5))

# Update for {n} monitoring sessions

for(i in 2:nsessions) {
  cat("Updating session ",i,"\n")
  res= calc.erad(rast, nsims, updated.priors, params)
  updated.priors<- calc.beta.parms(res$P.erad)
  mat[i,]<- c(i,median(res$P.erad),quantile(res$P.erad,c(0.025,0.975)))
}

mat<- as_tibble(mat)

```

### Optimal amount of monitoring

```{r, echo=FALSE}
nmin<- min(which(mat$P.erad > thresh.pfree))
if(is.finite(nmin)) cat(paste("Minimum number of repeat monitors with current sample size is ",nmin),"\n")
if(!is.finite(nmin)) cat(paste("Threshold not reached in ",nsessions," sessions"),"\n")
```

### Plot results

The plot below shows the relationship between the number of repeat monitors and the probability of pest eradication.

```{r, fig.height=6, fig.width=6, echo=FALSE}
p2<- mat %>% ggplot(aes(Session)) +
      geom_ribbon(aes(ymin=LCL,ymax=UCL),fill="grey70") +
      geom_line(aes(y=P.erad), size=1.5) +
      labs(x="Session",y="Probability of Eradication") +
      geom_hline(yintercept=thresh.pfree, linetype=2, colour="red", size=1.5)
p2
```

### Plot of System sensitivity
```{r, fig.height=6, fig.width=6, echo=FALSE, warning=FALSE}
tmp<- data.frame(SSe=res$SSe)
p3<- tmp %>% ggplot(aes(SSe)) +
      geom_histogram(binwidth=0.01, fill="lightblue", colour="black") +
      labs(x="SSe",y="Frequency")
      xlim(0, 1)
p3
```

Average SSe is `r round(mean(tmp$SSe),3)` with 95% Confidence intervals of `r round(quantile(tmp$SSe, 0.025),3)` - `r round(quantile(tmp$SSe, 0.975),3)`


```{r, fig.height=6, fig.width=6, echo=FALSE}

tmp_rast<- raster_data(res$map)
p4<- region %>% ggplot() +
      geom_raster(aes(x, y, fill=value), data=tmp_rast, interpolate=F) +
      scale_fill_distiller(palette="Spectral",na.value="white",limits=c(0, 1)) +
      geom_sf(fill=NA) +
      labs(x="Easting",y="Northing",title="Map of system sensitivity (SSe)")
p4
```

