Implementation Phase
========================================================

The purpose of the implementation phase is to conduct repeated removals from the population until no more animals are detected.  This script takes data collected from each removal session to date and updates the estimate of the residual population size.  The model can also use up to two additional monitoring methods to detect the presence of individuals.  Future versions will also calculates an estimate of the effort required to remove the remaining individuals.

```{r read_functions, include=FALSE}
source("Framework_functions.r")
library(knitr)
library(raster)
library(sf)
library(tidyverse)

```

### Read in the region shapefile...

```{r}
region<- read_sf("Stuff/.","San_Nicolas_projected")
region<- filter(region, SP_ID==0)

area<- st_area(region)/1e6 #in km2
```

area of region is `r round(area,1)` km^2

### Read in the removal/monitoring data collected to date

Changes the filename below to point to the latest data update
```{r read_data}
filename<- "Stuff/removal_data.rds"
data<- readRDS(filename)

```
### Data summary
```{r data_summary,echo=FALSE,comment=""}
removed<- caps.summary(data)
nsess<- nrow(removed)
removed
```

### Plot of cumulative removals/effort curve

```{r cumplot, echo=FALSE, fig.height=6,fig.width=6}
par(pty='s')
plot(cumsum(removed$Effort),cumsum(removed$Removed),type='l',xlab="Cumulative effort",ylab="Cumulative removals")
```

### Update estimates

#### Update of the residual population size

```{r estimates,echo=FALSE, message=FALSE}
if(is.null(data$cam.mon) & is.null(data$sign.mon)){
  cat("No camera or Sign monitoring present - using removal model only") 
  rem1<- Fit.RemMon(data)
}
if(!is.null(data$cam.mon) & is.null(data$sign.mon)) {
  cat("Camera monitoring present - using removal + camera monitoring model") 
  rem1<- Fit.OneMon(data, type="cams")
}
if(is.null(data$cam.mon) & !is.null(data$sign.mon)) {
  cat("Sign monitoring present - using removal + sign monitoring model") 
  rem1<- Fit.OneMon(data, type="sign")
}
if(!is.null(data$cam.mon) & !is.null(data$sign.mon)) {
  cat("Camera and Sign monitoring present - using removal + camera + sign monitoring model") 
  rem1<- Fit.BothMon(data)
}
cat(paste("Residual population size = ",round(rem1$q50$Nresid)," with 95% credible interval of ",round(rem1$q2.5$Nresid),"-",round(rem1$q97.5$Nresid),sep=""),"\n")
```

#### Update of the total population size
```{r totalpop,echo=FALSE}
cat(paste("Total population size = ",round(rem1$q50$N0)," with 95% credible interval of ",round(rem1$q2.5$N0),"-",round(rem1$q97.5$N0),sep=""),"\n")

```
#### Progress to date

Plot of the reduction in true population size against removal session (+/- 95% Credible intervals)

```{r progress, echo=FALSE, fig.width=6,fig.height=6}
par(pty="s")
plot(1:nsess,rem1$mean$N,type='l',xlab="Session number",ylab="Population size",ylim=c(0,rem1$mean$N[1]))
lines(1:nsess,rem1$q2.5$N,lty=2)
lines(1:nsess,rem1$q97.5$N,lty=2)
abline(h=rem1$mean$Nresid,col="red")
text(4,rem1$mean$Nresid+3,paste("residual pop now ",round(rem1$mean$Nresid)),cex=0.8)




```

