Pre-implementation
========================================================

The objective of the pre-implementation stage is to provide an initial estimate of population size/density.  This script estimates density using data from 'point counts'.  Two methods are used the 'N Mixture model' and the 'Royle/Nichols model'  

### Read in the data and analysis toolset

```{r}
counts<- as.matrix(read.csv("pcounts.csv"))
# read in toolset
source("Framework functions.r")
```

The number of cameras in this dataset is `r dim(counts)[1]`

The number of days exposure for this dataset is `r dim(counts)[2]`

### Set the total number of sampling quadrats on the island
```{r setparams}
nq<- 58

```


a quick look at the data:
-------------------------
```{r createtable, results='asis',echo=FALSE}
# Number of individuals/visits per camera
df<- apply(counts,1,sum)
df<- cbind(1:dim(counts)[1],df)
cat("Device | detections", "---------- | -------",sep="\n")
cat(apply(df,1,function(X) paste(X, collapse=" | ")),sep="\n")

```

### Run the N-mixture model.  

This model assumes that each count is the number of individuals observed

```{r, echo=FALSE}

fit1<- Fit.NmixModel(counts, nq)
cat(paste("Population size = ",round(fit1["PopEst",1])," with 95% credible interval of ",round(fit1["PopEst",3]),"-",round(fit1["PopEst",5]),sep=""),"\n")
```

### Run the RN Model.  
This model reduces the data to presence/absence per camera per night

```{r, echo=FALSE}

fit2<- Fit.RNModel(counts, nq)
cat(paste("Population size = ",round(fit2["PopEst",1])," with 95% credible interval of ",round(fit2["PopEst",3]),"-",round(fit2["PopEst",5]),sep=""),"\n")
```
