---
output:
  html_document: default
  pdf_document: default
---
Pre-implementation
========================================================

The objective of the pre-implementation stage is to provide an initial estimate of population size/density.  This script estimates density using data from 'point counts'.  Two methods are used the 'N Mixture model' and the 'Royle/Nichols model'  Both these models will be biased if average home range size differs markedly from the set cellsize.  Future versions will use more robust models for estimation

```{r setup, include=FALSE}
library(knitr)
library(raster)
library(sf)
library(tidyverse)
library(R.utils)
library(kableExtra)
```
### Load functions and Read in region shapefile ...

```{r}
source("Framework_functions.R")
region<- read_sf("Stuff","San_Nicolas_projected")
```

### rasterize the region to get sampling quadrats and select a random sample 

```{r}
res<- 1000 # cell size in meters
nsamp<- 30 # number of sampled cells
```

The region has been divided up into cells of size `r res` meters and a radom sample of `r nsamp` cells will be selected

```{r, echo=F, message=F}
bb<- st_bbox(region)
rast<- raster(xmn=bb$xmin,xmx=bb$xmax,ymn=bb$ymin,ymx=bb$ymax,resolution=res)
rast<- rasterize(region, rast, field=1)
rast_df<- raster_data(rast)
rcells<- as_tibble(sampleRandom(rast, size=nsamp, xy=TRUE))

p1<- region %>% ggplot() +
  geom_sf() +
  geom_tile(aes(x, y, fill=value), color="grey50", data=rast_df, show.legend = F) +
  scale_fill_gradientn(colors="lightblue",na.value="white") +
  geom_point(aes(x,y),data=rcells) +
  geom_sf(fill=NA) +
  labs(x="Easting",y="Northing",title="Quadrats in sampled Region - black points denote sampled quadrats")
p1

saveRDS(rast, "Results/rast.rds") # Save raster for decision support phase
```

### Read in the data 

```{r}
counts<- readRDS("Stuff/pcounts.rds")

```

The number of cameras in this dataset is `r dim(counts)[1]`

The number of days exposure for this dataset is `r dim(counts)[2]`

### Get the total number of sampling quadrats on the island
```{r setparams}
nq<- sum(rast_df$value, na.rm=TRUE)

```

The total number of quadrats in the region is `r nq`

a quick look at the data:
-------------------------
```{r createtable, results='asis',echo=FALSE}
# Number of individuals/visits per camera
df<- apply(counts,1,sum)
df<- tibble(Camera=1:dim(counts)[1],Visits=df)
kable(df, row.names = FALSE, caption = "Camera summary", format="html",align="c") %>% 
  kable_styling(bootstrap_options="striped", font_size=12)

```

### Run the N-mixture and RN models.  

N-mixture model assumes that each count is the number of individuals observed

RN model model reduces the data to presence/absence per camera per night

```{r, include=F}
est1<- Fit.NmixModel(counts, nq, n.iter=20000, n.burn=10000, n.chains=3)
est2<- Fit.RNModel(counts, nq, n.iter=20000, n.burn=10000, n.chains=3)

saveRDS(est2, "Results/est2.rds")  # Save results for decision support phase
```

### N-mixture estimate.  

```{r, echo=FALSE, message=FALSE}

cat(paste("Population size = ",round(est1["PopEst","mean"])," with 95% credible interval of ",
          round(est1["PopEst","2.5%"]),"-",round(est1["PopEst","97.5%"]),sep=""),"\n")

```

### RN estimate
```{r, echo=F, message=F}
cat(paste("Population size = ",round(est2["PopEst","mean"])," with 95% credible interval of ",
          round(est2["PopEst","2.5%"]),"-",round(est2["PopEst","97.5%"]),sep=""),"\n")
```

